\documentclass[letterpaper]{deedy-resume-modified} % Use US Letter paper, change to a4paper for A4 
\usepackage{enumitem}
\begin{document}
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------
\namesection{Tristan}{Amini}{ 
 (416) 801-5288 | tristanamini@gmail.com
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------
\hspace{-30pt}\colorbox{MidnightBlue!80}{\hspace{10pt}
\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page
\vspace{5pt}
%------------------------------------------------
% Education
%------------------------------------------------

\section*{\color{White}Education} 

\subsection*{\color{White}University of Waterloo}

\subsub{Bachelor of Applied Science}
\descript{\color{White}Systems Design Engineering}
\descript{\color{White}Class of 2018}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

\section*{\color{White}Connect} 

\subsub{Github: \href{https://github.com/Tamini}{github.com/Tamini}}
\subsub {LinkedIn: \href{https://www.linkedin.com/in/tamini}{linkedin.com/in/tamini}}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section*{\color{White}Technical Skills}
\vspace{2pt}

\subsection{\color{White}C++}
\vspace{5pt}
\quotext{\textbullet  Worked in \CPP \hspace{1pt} for driver dev at AMD.}
\vspace{3pt}
\quotext{\textbullet  Created KMD fuzz tester at AMD.}
\vspace{3pt}
\quotext{\textbullet  Used in game AI development at EA.}
\sectionspace %whitespace

\subsection{\color{White}Java}
\vspace{5pt}
\quotext{\textbullet  Created AntiChess and others games.}
\vspace{3pt}
\quotext{\textbullet  Utilized in Selenium tests at Polar.}
\vspace{3pt}
\quotext{\textbullet  Used in website backend at Interset.}

\sectionspace %whitespace

\subsection{\color{White}JavaScript}
\vspace{5pt}
\quotext{\textbullet  Worked heavily in JavaScript at Uber.}
\vspace{3pt}
\quotext{\textbullet  Created many data visualizations.}
\vspace{3pt}
\quotext{\textbullet  Thorough understanding of React.}

\sectionspace %whitespace

\subsection{\color{White}SQL}
\vspace{5pt}
\quotext{\textbullet  Wrote scripts to dump SQL at Polar.}
\vspace{3pt}
\quotext{\textbullet  Setup/maintain SQL stack at Interset.}
\vspace{3pt}
\quotext{\textbullet  Shifted NHL AI backend to SQL at EA.}
\sectionspace

\subsection{\color{White}Python}
\vspace{5pt}
\quotext{\textbullet  Wrote bot for Polar's internal IRC.}
\vspace{3pt}
\quotext{\textbullet  Worked with Django at Polar.}
\vspace{3pt}
\quotext{\textbullet  Write scripts to speed up school work.}
\sectionspace

\subsection{\color{White}MATLAB}
\vspace{5pt}
\quotext{\textbullet  Learned in university courses.}
\vspace{3pt}
\quotext{\textbullet  Utilized for signal processing.}
\vspace{3pt}
\quotext{\textbullet  Simulated projects for ideal results.}
\sectionspace

\subsection{\color{White}Additional Skills}
\vspace{5pt}
\quotext{Git, \LaTeX, Scala, Go, Blender, Maya, Unreal Engine 4, x86 Assembly}
\sectionspace

%------------------------------------------------
% Past Employers
%------------------------------------------------
%\vspace{-5pt}
%\section*{\color{White}Past Employers}
%\subsection{\color{White}Interset}
%\quotext{"...he demonstrated an exceptional ability to very quickly become productive with new technologies." }
%\subsub{- Michael Iles | Dev Lead}
%\vspace{7pt}
%\subsection{\color{White}IBM}
%\quotext{"...his innovative solution to managing exceptions and frame descriptors was the key to our finishing that project..."}
%\subsub{- Bill O'Farrell | Developer}
%\vspace{5pt}

%\section*{\color{White}ADDITIONAL INFO}
%\quotext{Although my past internships have been mostly software focused, I am also quite good with electronics. I have taken multiple courses %that have given me hands-on experience with circuits. I know how to solder and have made use of it in past projects.}
%\vspace{16pt}


%\subsub{This resume is written in \LaTeX! \vspace{1pt} View the source at: \href{https://github.com/Tamini/Resume} %{github.com/Tamini/Resume}}
\vspace{80pt}
\end{minipage}} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
\changeurlcolor{Black}
\vspace{5pt}
%------------------------------------------------
% Experience
%------------------------------------------------

\section{Work Experience}

\runsubsection{Uber}
\descript{| Software Engineering Intern - Maps}

\location{May 2017 - August 2017 | San Francisco, CA}
\vspace{\topsep}
\begin{tightitemize}
\item Constructed vector tiles in Java to pass to the web frontend in order to display desired information on maps using MapBox.
\item Set up S3 bucket, JavaScript frontend and Java backend to allow for uploading and displaying of images on the web pages.
\item Set up a variety of dynamic data visualizations by surfacing ElasticSearch data to the JavaScript/React/Redux frontend.
\end{tightitemize}

\sectionspace %whitespace

%----------------------------------------------
\runsubsection{Electronic Arts}
\descript{| Associate Developer - Gameplay}
\location{September 2016 - December 2016 | Burnaby, BC}
\vspace{\topsep}
\begin{tightitemize}
\vspace{-10pt}
\item Suggested and implemented SQLite to store different AI sequences for use in-game and to speed up development time.  
\item Rewrote much of the legacy \CPP \hspace{1pt}code for new read and write operations.
\item Created a set of placers and processors in C\# to organize, expediate and improve the animation selection process.
\end{tightitemize}

\sectionspace %whitespace

%----------------------------------------------

\runsubsection{AMD}
\descript{| Driver Developer}

\location{January 2016 - April 2016 | Markham, ON}
\vspace{\topsep}
\begin{tightitemize}
\vspace{-10pt}
\item Led the team that developed software in \CPP \hspace{1pt} to simulate attacks on potential vulnerabilities in the AMD display driver.  Leading to a more secure and reliable driver for AMD's users.
\item Fixed bugs and worked on features in the AMD Kernel Mode Driver.
\end{tightitemize}

\sectionspace %whitespace

%----------------------------------------------

\runsubsection{IBM}
\descript{| Open Source Compiler Developer}

\location{May 2015 - August 2015 | Markham, ON}
\begin{tightitemize}
\item Part of the two-man team that ported the OCaml compiler to the Z Architecture. Required writing x64, PPC and Z Assembly.
\end{tightitemize}

\sectionspace %whitespace

%----------------------------------------------

\runsubsection{Interset}
\descript{| Software Engineer}

\location{September 2014 – December 2014 | Ottawa, ON}
\begin{tightitemize}
\item Created Scala application to read and anonymize millions of data entries.
\item Maintained and set up a Hadoop/HBase/Phoenix/Spark install on AWS.
\item Built company web pages using JavaScript, HTML and CSS.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Polar}
\descript{| DevOps}

\location{January 2014 - April 2014 | Toronto, ON}
\begin{tightitemize}
\item Worked with Django and python for Polar's website and product backend.
\item Created MySQL dump scripts in Python and SQL that run daily using cron.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Open Source Work
%------------------------------------------------
%\vspace{-8pt}
%\section{Open Source Work}

%\runsubsection{Jenkins}
%\descript{| Contributing Community Member}

%\location{March 2014 - Present  |  \href{www.jenkins.io}{jenkins.io}}
%Fixed a bug in the Cobertura plugin that caused test result metrics to be incorrectly displayed to users.

%\sectionspace % Some whitespace after the section



%------------------------------------------------
% Personal Projects
%------------------------------------------------
\vspace{-8pt}
\section{Personal Projects}

\runsubsection{Spark}
\descript{| Third-Person Hack and Slash Game}

\location{July 2016 - Present  |  Still in development!}
Creating a third-person PC game in Unreal Engine 4 using both Blueprints and C++.  Using Blender for modelling and Maya for animation.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{AntiChess}
\descript{| Chess Game with Custom AI}

\location{2012 - 2013 | \href{https://github.com/Tamini/AntiChess} {github.com/Tamini/AntiChess}}
Created a chess game in Java with a from scratch custom AI. The AI determined the best move by looking at possible future board states, pruning very undesirable states early to save processing time.


\sectionspace % Some whitespace after the section

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
