\documentclass[letterpaper]{deedy-resume-modified} % Use US Letter paper, change to a4paper for A4 

\begin{document}
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\namesection{Tristan}{Amini}{ 
 (416) 801-5288 | tsamini@uwaterloo.ca
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------
\hspace{-30pt}\colorbox{MidnightBlue!80}{\hspace{10pt}
\begin{minipage}[t]{0.32\textwidth} % The left column takes up 33% of the text width of the page
\vspace{16pt}
%------------------------------------------------
% Education
%------------------------------------------------

\section*{\color{White}EDUCATION} 

\subsection*{\color{White}University of Waterloo}

\descript{\color{White}Systems Design Engineering}
\subsub{Class of 2018}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

\section*{\color{White}LINKS} 

\subsub{Github: \href{https://github.com/Tamini}{github.com/Tamini}}
\subsub {LinkedIn: \href{https://www.linkedin.com/in/tamini}{linkedin.com/in/tamini}}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section*{\color{White}PROGRAMMING}
\subsub {Language | Proficiency}
\NumTabs{3}
\vspace{2pt}
\listplus{Java}{+ + + +}
\listplus{\CPP}{+ + + +}
\listplus{Go}{+ + +}
\listplus{\LaTeX}{+ + +}
\listplus{OCaml}{+ + +}
\listplus{Scala}{+ + +}
\listplus{SQL}{+ + +}
\listplus{Python}{+ + +}
\listplus{MATLAB}{+ + +}
\listplus{R}{+ + +}
\listplus{Assembly}{+ +}
\listplus{Chef}{+ +}
\listplus{Ruby}{+ +}

\sectionspace
\subsub {Tool | Proficiency}
\listplus{Git}{+ + + +}
\listplus{Jira}{+ + + +}
\listplus{gdb}{+ + + +}
\listplus{Jenkins CI}{+ + + +}
\listplus{WinDebug}{+ + +}
\listplus{Perforce}{+ + +}
\listplus{Maven}{+ + +}
\listplus{Android}{+ + +}

\sectionspace

%------------------------------------------------
% Past Employers
%------------------------------------------------

\section*{\color{White}PAST EMPLOYERS}
\subsection{\color{White}Interset}
\quotext{"...he demonstrated an exceptional ability to very quickly become productive with new technologies." }
\subsub{- Michael Iles | Dev Lead}
\vspace{7pt}
\subsection{\color{White}IBM}
\quotext{"...his innovative solution to managing exceptions and frame descriptors was the key to our finishing that project..."}
\subsub{- Bill O'Farrell | Developer}
\vspace{20pt}

\subsub{This resume is written in \LaTeX! \vspace{1pt} Find the source at: \href{https://github.com/Tamini/Resume}{github.com/Tamini/Resume}}
\vspace{25pt}
\end{minipage}} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
\changeurlcolor{Black}
\vspace{16pt}
%------------------------------------------------
% Experience
%------------------------------------------------

\section{WORK EXPERIENCE}

\runsubsection{AMD}
\descript{| Driver Developer}

\location{January 2016 - April 2016 | Markham, ON}
\vspace{\topsep}
\begin{tightitemize}
\item Fixed bugs in the AMD Kernel Mode Driver for Windows 7, 8.1 and 10.
\item Led the team that created a \CPP \hspace{1pt} program to simulate attacks on the AMD display driver.  Fixed all identified security vulnerabilities leading to a more secure and reliable driver for AMD's users.
\end{tightitemize}

\sectionspace %whitespace

\runsubsection{IBM}
\descript{| Open Source Compiler Developer}

\location{May 2015 - August 2015 | Markham, ON}
%\vspace{\topsep}
\begin{tightitemize}
\item Part of the two man team that ported the OCaml compiler to the Z Architecture. Required reading and writing x64, PPC and Z Assembly.
\item Wrote a relocation type for the Go linker to work with Z.
\item Worked on the Go Assembler for Z.
\end{tightitemize}

\sectionspace %whitespace

%----------------------------------------------

\runsubsection{Interset}
\descript{| Software Engineer}

\location{September 2014 – December 2014 | Ottawa, ON}
\begin{tightitemize}
\item Wrote bash script to allow for automatic OVA creation for customer deployments of software bundle.
\item Created Scala application to read and anonymize millions of data entries.
\item Maintained and set up a Hadoop/HBase/Phoenix/Spark install on AWS.
\item Built web pages for use internally and by customers.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Polar}
\descript{| DevOps}

\location{January 2014 - April 2014 | Toronto, ON}
\begin{tightitemize}
\item Set up easily recreatable and destroyable virtual machines using Chef.
\item Created MySQL dump scripts in Python and SQL that run daily using cron.
\item Wrote an IRC bot in Python to help coordinate users and add useful features to the IRC chat.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Open Source
%------------------------------------------------

\section{OPEN SOURCE WORK}

\runsubsection{Jenkins CI}
\descript{| Contributing Community Member}
\location{March 2014 – Present | \href{http://www.jenkins-ci.org} {www.jenkins-ci.org}}
\begin{tightitemize}
\item Fixed a bug in the Cobertura plugin which required use of Java and Maven.
\item Updated the Jira plugin to use a better method for building strings.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Personal Projects
%------------------------------------------------

\section{PERSONAL PROJECTS}

\runsubsection{Spark}
\descript{| Third-Person Hack and Slash Game}

\location{March 2016 - Present  |  Still in development!}
Creating a third-person PC game in Unreal Engine 4 using Blueprints and C++.  Currently have enemy NPCs, basic animations and basic combat.  Will require working with game AI, animating, modelling, texturing and programming.  

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{AntiChess}
\descript{| Chess Game}

\location{2012 - 2013 | \href{https://github.com/Tamini/AntiChess} {github.com/Tamini/AntiChess}}
Created a chess game in Java with a custom AI in Java.   AI implemented alpha-beta pruning and depth-first search to find the best moves.


\sectionspace % Some whitespace after the section

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}